Neural models for computer-assisted musical orchestration: a preliminary study

### 2020-05-12 paper/latex/paper.tex
Redo commit 'Add orch eval table'

\begin{table}
  \begin{center}
    \label{tab:table1}
    \begin{tabular}{c|c|c|c} 
    	  \hline
      \textbf{Instr. 1} & \textbf{Instr. 2} & \textbf{SVM Accuracy} & \textbf{RF Accuracy}\\
      \hline
      Violin & Flute & 38.8\% & 9.8\% \\
      \hline
      Violin & Trumpet & 33.8\% & 9.1\% \\
      \hline
      Violin & Cello & 34.8\% & 6.3\% \\
      \hline
      Cello & Viola & 32.1\% & 5.8\% \\
      \hline
      Oboe & French Horn & \textbf{39.9\%} & \textbf{17.5\%} \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Comparison of results between SVM and Random Forest. Each data point is a combination of two TinySOL samples, where at least one of the samples is from one of the two instruments specified for that experiment. For the samples drawn from one of the two instruments, the pitch class of that sample is identified. For a sample not from one of the two instruments, the classifier simply attempted to identify that a sample from one of the non-specified instruments was present. In this setting, there are 25 classes: 24 from the 12 pitch classes from 2 instruments, and 1 class that specified whether an instrument that is not one of the two specified is present.}
\end{table}

@@

@@

\textbf{(Add results of quantitatively comparing our results to OrchIdea)}

>>>>

\begin{table}
  \begin{center}
    \label{tab:table1}
    \begin{tabular}{|c|c|c|c|} 
    	  \hline
      \textbf{Instr. 1} & \textbf{Instr. 2} & \textbf{SVM Accuracy} & \textbf{RF Accuracy}\\
      \hline
      Violin & Flute & 38.8\% & 9.8\% \\
      \hline
      Violin & Trumpet & 33.8\% & 9.1\% \\
      \hline
      Violin & Cello & 34.8\% & 6.3\% \\
      \hline
      Cello & Viola & 32.1\% & 5.8\% \\
      \hline
      Oboe & French Horn & \textbf{39.9\%} & \textbf{17.5\%} \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Comparison of results between SVM and Random Forest. Each data point is a combination of two TinySOL samples, where at least one of the samples is from one of the two instruments specified for that experiment. For the samples drawn from one of the two instruments, the pitch class of that sample is identified. For a sample not from one of the two instruments, the classifier simply attempted to identify that a sample from one of the non-specified instruments was present. In this setting, there are 25 classes: 24 from the 12 pitch classes from 2 instruments, and 1 class that specified whether an instrument that is not one of the two specified is present.}
\end{table}

@@

In order to have comparable solutions, we did not allow OrchIdea to create sparse solutions, meaning that OrchIdea was forced to use all 10 instruments in each solution. This creates a more fair comparison since our model is optimize solutions by using fewer than 10 samples.

@@

\begin{table}
  \begin{center}
    \label{tab:table2}
    \begin{tabular}{|c|c|} 
    	  \hline
      \textbf{Model} & \textbf{Average Distance} \\
      \hline
      CNN with LSTM &   \\
      \hline
      ResNet &  \\
      \hline
      OrchIdea &  \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Comparison of the orchestration solutions of our two models, CNN with LSTM and ResNet, against OrchIdea's solutions. The distance between the target and solution are calculated for each target using \eqref{distance} and then averaged.}
\end{table}
